UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio and Reconfigurable Intelligent Surface

### 2022-08-20 main.tex
:pencil: Add challenges of decision threshold design

	\begin{subsection}{Decision Threshold}
		For any given $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$ and $\boldsymbol{w}$, problem \eqref{op:weighted_sum_rate} reduces to
		\begin{maxi!}
			{\scriptstyle{\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:decision_threshold}}{\label{ob:decision_threshold}}
			\addConstraint{\eqref{co:decision_threshold},}
		\end{maxi!}
		and it is trivial to conclude $t_0^\star=0$ and $t_L^\star=\infty$ for energy-based backscatter detection.

@@

>>>>

	\begin{subsection}{Decision Threshold}
		For any given $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$ and $\boldsymbol{w}$, problem \eqref{op:weighted_sum_rate} reduces to
		\begin{maxi!}
			{\scriptstyle{\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:decision_threshold}}{\label{ob:decision_threshold}}
			\addConstraint{\eqref{co:decision_threshold},}
		\end{maxi!}
		which is still non-convex because variable $\boldsymbol{t}$ appear on the limits of integration \eqref{eq:dmtmac}.
		% % To tackle this, we 1) reveal backscatter decision design has no impact on primary decoding, 2) constrain the feasible domain of problem \eqref{op:decision_threshold} from continuous space $\mathbb{R}_+$ to finite candidate set (i.e., fine-grained discrete output energy levels) $\mathcal{T}$,
		% To tackle this, we 1) reveal backscatter decision design has no impact on primary decoding, 2) constrain the feasible domain of problem \eqref{op:decision_threshold} from continuous space $\mathbb{R}_+$ to finite candidate set of fine-grained discrete output energy levels $\mathcal{T}$, 3) regard UniScatter nodes with given input distribution as an equivalent augmented source in terms of total backscatter rate, 4) reuse existing quantization schemes for \gls{dmc} to solve problem \eqref{op:decision_threshold}.
		% % 3) indicate the equivalence between multi and single in terms of total backscatter rate
		% % 3) regard all UniScatter nodes as an equivalent augmented source in terms of total backscatter rate
		To tackle this, we first reveal backscatter decision design has no impact on primary decoding, then constrain the feasible domain of problem \eqref{op:decision_threshold} from continuous space $\mathbb{R}_+$ to finite candidate set (i.e., fine-grained discrete energy levels) $\mathcal{T}$.
		We also point out distributed nodes with given input distribution is equivalent to an augmented source of symbol tuples in terms of total rate, and reuse existing rate-optimal quantization schemes for \gls{dmc} to solve problem \eqref{op:decision_threshold}.

@@

		where $t_0^\star=0$ and $t_L^\star=\infty$ for energy-based backscatter detection.
